Draft

### 2017-08-28 Thesis/Draft.Rmd
Edit AugUCB chapter

@@

In the case of $\tau = 0.5$, the latter KL-divergence is symmetric in its first argument, and thus can be relatively well approximated by Pinsker's inequality (SHOW IN GRAPH!):

@@

```{r, echo = FALSE}
KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
par(mfcol = c(1,2))

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
     xlab = "p_1", ylab = "KL(Ber(p_1),Ber(p_2))", main = "KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
       KL_ber(seq(0.00001,0.3, by = 0.000005),i))
}

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
     xlab = "p_1", ylab = "(p_1 - p_2)^2", main = "Gaussian approx.\n KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
        (seq(0.00001,0.3, by = 0.000005)-i)^2)
}
par(mfcol = c(1,1))
```

```{r, echo = FALSE}
KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
par(mfcol = c(1,2))

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
     xlab = "p_1", ylab = "KL(Ber(p_2),Ber(p_1))", main = "KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
        KL_ber(i,seq(0.00001,0.3, by = 0.000005)))
}

plot(x = 1, y = 1, xlim = c(0, 0.3), ylim = c(0, 1), type = "n", asp = 1,
     xlab = "p_1", ylab = "(p_2 - p_1)^2", main = "Gaussian approx.\n KL of Bernoullis")
for(i in c(0.0001,0.001, 0.005,0.01,0.05,0.1)) {
  lines(seq(0.00001,0.3, by = 0.000005),
        (i-seq(0.00001,0.3, by = 0.000005))^2)
}
par(mfcol = c(1,1))
```

@@

where $\bm{\lambda}$ is the vector of means defining the distributions of the alternative problem to $\bm{\mu}$. Lastly, we have the set of probability distributions on the arms $\mathcal{A}$: $\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}$. \marginpar{Give more intuition for what these probability distributions are} We are now ready to state the theorem.

@@

# Extensions to the Thresholding Bandit Problem

## Introduction

We have introduced the thresholding bandit problem in chapter 1. The APT algorith described in Locatelli et al. (2016) is able to match a lower bound (be more specific!) given in the same paper, and has several favorable characteristics such as its overall simplicity and it being an anytime algorithm. However, the bounds on the expected loss assume the arms' distributions to be $R$-sub-Gaussian. This is reflected in the algorithm's complexity measure $H = \sum_{i=1}^K (\Delta_i^{\tau, \epsilon})^{-2}$, where $\Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon$, which -- given the known threshold $\tau \pm \epsilon$ -- only depends on the distribution's mean. This is appropriate for Gaussian arms with equal variances, but potentially inefficient for other kinds of distributions.

@@

In the case of Gaussians, the complexity $H$ is nice also because it reflects the Kullback-Leibler divergence between two Gaussians. And since Bernoulli distributions are bounded on the interval $[0,1]$, they are consequently sub-Gaussian, meaning that their Kullback-Leibler divergence can be approximated by the Gaussian one. However, while Bernoullis are sub-Gaussian, the approximation of their divergence by the Gaussian divergence becomes less and less optimal as the parameter (and thus mean) goes to $0$ or $1$, as shown in chapter 1. And while online advertisements might not be an obvious use case for thresholding bandits, they are just one real life scenario dominated by Bernoulli distributions with very small parameters. Thus it is worthwile to adapt current solutions of the thresholding bandit problem to cases in which the Gaussian Kullback-Leibler divergence is no longer an appropriate approximation.

Large motiviation for the idea of adjusting the complexity measure (and thus the algorithms) to distributions more generally based on the Kullback-Leibler divergence stems from the work discussed in chapter 2, complexity measures were defined for the pure exploration bandits in terms of the Kullback-Leibler divergence. Based on this, the authors were for example able to point our differences between Gaussian and Bernoulli bandits. We expect that results in a similar vain could be derived for thresholding bandits.

To this end, in the following, we first present an extension of mean based algorithms to an algorithm that incorporates empirical variances as described in Mukherjee et al. (2017). Afterwards, we propose and discuss potential further improvements based on Kullback-Leibler divergence and Bayesian posterior distributions. Finally, we compare the performance of different algorithms based on simulations and real world data sets.

## Variance Based Algorithms for Thresholding Bandits \label{chap:VarianceBasedAlgorithms}

@@

Mukherjee et al. (2017) propose an algorithm based on variance estimates called Augmented-UCB (AugUCB). The setting in which the algorithm is proposed is very similar to the setting in Locatelli et al. (2016). The algorithm itself, however, differs heavily from the APT algorithm. So is AugUCB for example not an anytime algorithm. Furthermore, arms can be deleted in every round if there are "far enough" away from the mean. Both the decision of which arm is played in a given round, and whether an arm is removed from the active set of arm, is based not only on the empirical mean estimate $\mu_i(t)$, but also on a term $s_i$ that is increasing linearly in the estimated standard deviation. While the APT algorithm plays the arm minimizing the quantity $B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)$, AugUCB plays the arm minimizing the quantity $(\hat{\Delta}_i(t) - 2s_i)$, where $s_i$ is based on the variance estimate $\hat{v}_i$, and an exploration $\psi_m$ term linear in $T$, and an elimination parameter $\rho$ (compare Algorithm 1 in Mukherjee et al., 2017):

\begin{equation*}
s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}
\end{equation*}

Consequently, the authors also introduce complexity measures which take the variance into account. From Gabillon et al. (2011) they use $H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}$. Furthermore, with $\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}$, and with $\stackrel{\sim}{\Delta}_{(i)}$ being an increasing ordering of $\stackrel{\sim}{\Delta}_i$, the authors define a complexity corresponding to $H_{CSAR,2}$ in Chen et al. (2014):

\begin{equation*}
H_{\sigma,2} = \max_{i \ in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
\end{equation*}

While the latter complexity appears in the provided upper bound on the AugUCB algorithm's expected loss, it could be replaced by $H_{\sigma, 1}$ since $H_{\sigma, 2} \leq H_{\sigma,1}$. $H_{\sigma,1}$ is of course more directly comparable to the complexity $H$ that we are used to.

While in the case of the APT algorithm the number of times a specific arm has been drawn $T_i$ measures how concentrated the estimated mean is around the true mean (and thus for large $T_i$ an arm is no longer drawn even if $\hat{\mu}$ is close to $\tau$); in the case of the AugUCB algorithm this is regulated by the combination of the variance estimate $\hat{v}_i$ and the exploration factor $\psi_m$, where they ensure that certain arms are no longer pulled when the algorithm is sufficiently confident in its knowledge about the true mean. Therefore, when using a very similar favorable event in the proof of their upper bound, Mukherjee et al. (2017) have to bound the probability that an an arm is not removed from the active set after the a certain number of rounds -- even though the arm is above (respectively below) the threshold. If this probability is low, then this means that the algorithm is able to be certain about an arm's true mean *quickly* by employing variance estimates. In comparison, Locatelli et al (2016) used bounds on on how often arms are drawn ($T_i$) to give a bound on the probability of the favorable event. In order to derive the bound, Mukherjee et al. (2017) use the Bernstein inequality.

It has to be noted that Mukherjee et al. (2017) have to assume that the distributions have rewards bounded in $[0,1]$ in order to derive the bound on the probability that an arm has not been eliminated correctly in round $T_i$. Thus, the distributions for which their upper bound holds are a subset of the sub-Gaussian distributions considered in Locatelli et al. (2016). However, it is not that the authors need to assume that the rewards are in $[0,1]$, but this was assumed so that the variance of the distribution is in $[0,1]$. Thus, the upper bound holds in particular for Gaussian distributions with variance $\sigma^2 \in [0,1]$.

@@

Compare Mukherjee et al. (2017) for the notation. Then it becomes clear that the left part of the RHS gives the probability that the mean estimate is out of wack, while the right term gives the probability that the variance is overestimated. The first term is bounded by the Bernstein inequality. In the cumulative regret setting, there exists a similar decomposition that bounds the expected number of pulls of a suboptimal arm. Compare for example chapter 3.1 in "Thompson Sampling: An Asymptotically Optimal Finite Time Analysis" by Kaufmann, Korda and Munos (2012). There they decompose the expected number of draws of an suboptimal arm for an optimistic (UCB like) into the probability that the optimal arm's mean is underestimated, and the probability that the UCB of the suboptimal arm is still very large. To give bounds for UCB algorithms, it is then shown that these two terms show a certain convergence. Mukherjee et al. do similarly for their variance based algorithm in the thresholding setting.

(since the AugUCB eliminates arms, it is interesting to see how it behaves when the underlying CTR changes over time...)

-> Happens for exponential distribution

@@

```{r EVT_Index_Bernoulli, echo = FALSE}
bfun <- function(mu, tau) sqrt((mu*(1-mu))^2 + abs(tau-mu)) - mu*(1-mu)
plot(seq(0,1,0.0001), bfun(0,seq(0,1,0.0001)), type = "l",
     xlab = "Sample Mean", ylab = "Distance $D_i(t)$", main = "Variation over tau")
for(i in 1:length(seq(0,1,by=0.1))) {
  lines(seq(0,1,0.0001), bfun(seq(0,1,by=0.1)[i], seq(0,1,0.0001)), 
        col = rainbow(length(seq(0,1,by=0.1)))[i])
}
```

@@

```{r Hevt_Hapt_Comparison, echo = FALSE, message = FALSE}
hevt <- function(mu, tau) {
  (mu*(1-mu))^2 * (abs(mu-tau))^{-2} + abs(mu-tau)^{-1}
}

@@

plot(seq(0.1,0.9,0.0001), 
     hapt(seq(0.1,0.9,0.0001), 0.5), type = "l",
     ylim = c(0,400), ylab = "Complexity", xlab = "Bernoulli Mean",
     main = "APT vs EVT Complexity for tau = 0.5")
lines(c(seq(0.1,0.9,0.0001)), 
      hevt(c(seq(0.1,0.9,0.0001)), 0.5),
      col = "blue")
abline(v = 0.5, lty = 2)
```

@@

# Experiments

## Synthetic Data

@@

```{r simulation1_results, echo = FALSE}
library(ggplot2)
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR"), 
                   each = 1991), rep("B-UCB", 3991), rep("EVT", 1981))
index <- c(rep(10:2000, times = 4), 10:4000, 20:2000)
alg_res <- log(c(loc2_comp_UNIFORM_2000, loc2_comp_APT_2000, 
                 loc2_comp_AugUCB_2000, loc2_comp_LR_2000,
                 loc2_comp_BUCB_horizon_4000, loc2_comp_EVT))
loc2_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc2_comp_res, aes(x = index, y = results)) + 
  geom_line(aes(group = names, color = names)) +
  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  labs(title = "Results of Synthetic Experiment 1", 
       subtitle = expression(paste("Ideal scenario for APT; ", 
                                   tau,' = 0.5')), 
       y = "log(Error)", x = "Round Index") + 
  coord_cartesian(xlim = c(0,2000)) +
  scale_color_discrete(name = "Algorithm")

@@

```{r simulation2_results, echo = FALSE}
library(ggplot2)
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR", "B-UCB"), 
                   each = 6991), rep("EVT", 6981))
index <- c(rep(10:7000, times = 5), 20:7000)
alg_res <- log(c(loc6nt_comp_UNIFORM_7000, loc6nt_comp_APT_7000,
                 loc6nt_comp_AugUCB_7000, loc6nt_comp_LR_7000,
                 loc6nt_comp_BUCB_horizon_7000, loc6nt_comp_EVT))
loc6nt_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc6nt_comp_res, aes(x = index, y = results)) + 
  geom_line(aes(group = names, color = names)) +
  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  labs(title = "Results of Synthetic Experiment 2", 
       subtitle = expression(paste("Difficult scenario for APT; ", 
                                   tau,' = 0.05 and 10 arms. Dashed line at Error = 0.1.')), 
       y = "log(Error)", x = "Round Index") +
  scale_color_discrete(name = "Algorithm")
```

```{r, echo = FALSE, message = FALSE}
load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_ma.Rda")
library(dplyr)

rbind(loc6nt_APT_ma, loc6nt_LR_ma) %>%
  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
  geom_line(size = 0.3) +
  facet_grid(.~algorithm) +
  labs(x = "Index", y = "10 Rounds Moving Average",
       title = "Average Number of Pulls Allocated to Each Arm per Round",
       subtitle = "5000 iterations; a value of 1000 means that in 20% of 
the iterations the arm was pulled in that round.") +
  theme(legend.position = "bottom")

rbind(loc6nt_BUCB_c15_ma, loc6nt_BUCB_ma, loc6nt_BUCB_c5_ma) %>%
  ggplot(aes(x = index, y = mean, group = arm, color = arm)) +
  geom_line(size = 0.3) +
  facet_grid(.~algorithm) +
  labs(x = "Index", y = "10 Rounds Moving Average",
       title = "Average Number of Pulls Allocated to Each Arm per Round",
       subtitle = "5000 iterations; a value of 1000 means that in 20% of 
       the iterations the arm was pulled in that round.")+
  theme(legend.position = "bottom")
```

@@

```{r simulation3_results, echo = FALSE}
library(ggplot2)
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"

@@

```{r simulation4_results, echo = FALSE}
library(ggplot2)
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/exponential/"

@@

```{r simulation5_results, echo = FALSE}
library(ggplot2)
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/poisson/"

@@

```{r, echo = FALSE, message = FALSE}
library(zoo)
library(tidyr)
library(dplyr)
library(ggplot2)
load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo3_wide.Rda")

real_daily <- data.frame(index = 1:8641,
                                lapply(data_amo3_wide[1:10080,], FUN = rollapply, 
                                       width = 24*60, mean)) %>%
  gather(arm, mean, -index) %>%
  mutate(source = rep("Real", 86410))

>>>>

- Mention Optimality (Upper Bound matches lower bound)
- Anytime

@@

In the case of $\tau = 0.5$, the latter KL-divergence is symmetric in its first argument, and thus can be relatively well approximated by Pinsker's inequality:

@@

```{r KLApproximationComparison, echo = FALSE, message = FALSE, out.width = '80%', fig.align = "center", fig.cap= "The approximation of the Bernoulli KL-divergence by the Gaussian KL-divergence works well if the second argument is equal to 0.5. Else we observe poor approximation in both value and symmetry. This becomes more obvious as the arguments move away from 0.5."}
library(dplyr)
library(tidyr)
library(ggplot2)
KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
KL_gauss <- function(p,q) 2*(p-q)^2

kldf <- data.frame(mu = rep(seq(0.00001, 0.99999, 
                                length.out = 10000), 2),
                   tau = c(rep(0.5, 10000), rep(0.05, 10000)))

kldf_long <- kldf %>% mutate(Gaussian = KL_gauss(mu, tau),
                             Bernoulli = KL_ber(mu, tau)) %>%
  gather(key = KL_Type, value = KL, -mu, -tau) %>%
  mutate(tau = as.character(tau))

kldf2 <- data.frame(mu = rep(seq(0.00001, 0.09999, 
                                length.out = 10000), 1),
                   tau = c(rep(0.05, 10000)))

kldf2_long <- kldf2 %>% mutate(Gaussian = KL_gauss(mu, tau),
                              Bernoulli = KL_ber(mu, tau)) %>%
  gather(key = KL_Type, value = KL, -mu, -tau) %>%
  mutate(tau = as.character(tau))

kldf_total <- cbind.data.frame(level = c(rep("Global", 40000),
                                         rep("Local", 20000)),
                               rbind.data.frame(kldf_long, kldf2_long))

ggplot(kldf_total, aes(x = mu, y = KL, 
                      group = interaction(KL_Type, tau))) +
  facet_grid(level~., scales = "free") +
  geom_line(aes(color = tau, linetype = KL_Type)) +
  labs(x = "First argument of KL-divergence",
       y = "KL-divergence",
       title = "Comparison of Bernoulli KL-divergence and 
Gaussian Approximation")  +
  theme_bw() +
  theme(legend.position = "bottom") +
  scale_color_discrete(name = "Second argument of KL-divergence") +
  scale_linetype_discrete(name = "Type of KL-divergence") +
  guides(color = guide_legend(title.position = "top"),
         linetype = guide_legend(title.position = "top"))
```

@@

where $\bm{\lambda}$ is the vector of means defining the distributions of the alternative problem to $\bm{\mu}$. Lastly, we have the set of probability distributions on the arms $\mathcal{A}$: $\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}$. We are now ready to state the theorem.

@@

# Extensions to the Thresholding Bandit Problem \label{chap:Extensions}

## Introduction \label{sec:ExtensionsIntroduction}

In \autoref{chap:ThresholdingBanditProblem} we have introduced the thresholding bandit problem as proposed in Locatelli et al. (2016) alongside the APT algorithm. We have seen that the upper bound on the APT algorithm matches the lower bound for the thresholding bandit problem given in Locatelli et al. (2016). The algorithm also exhibits favorable characteristics such that its upper bound holds at any stopping time, and that it does not require any parameter to be known upfront. However, we have seen that the index and the complexity term $H$ employed by the APT algorithm are the most effective for $R$-sub-Gaussian distributions. Both are related to the KL-divergence between two Gaussian distributions of equal variance. Given that this sub-Gaussian approximation can be poor in certain cases, we motivated the use of information theoretic measures in an algorithm's index (compare \autoref{sec:DiscussionLocatelli}).

Another goal can be to compare the distributions with the threshold based not only on the empirical mean -- as done by the APT algorithm. A logical extension is for example the empirical variance. After all arms do not necessarily have the same variance, even if they are sub-Gaussian. And given two arms for which we estimate the same mean, we would prefer to draw more samples from the arm with the larger variance.

@@

For these reasons, in the following, we first present in \autoref{sec:VarianceBasedAlgorithms} two algorithms which incorporate empirical variances as described in Mukherjee et al. (2017) and Zhong et al. (2017). We then introduce a new algorithm based on the concept of likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}. Finally, we compare the performance of different algorithms based on simulations and real world data sets in \autoref{chap:Experiments}.

## Variance Based Algorithms for the Thresholding Bandit \label{sec:VarianceBasedAlgorithms}

@@

Combining learnings from the APT and other algorithms, Mukherjee et al. (2017) propose the Augmented-UCB (AugUCB) algorithm based on variance estimates for the thresholding bandit problem. The setting they consider is thus very similar to the setting in Locatelli et al. (2016). The main difference being that, while Locatelli et al. (2016) assume $R$-sub-Gaussian reward distributions, Mukherjee et al. (2017) assume rewards to be bounded in $[0,1]$, which makes the AugUCB applicable to less distributions. The AugUCB algorithm itself differs significantly from the APT algorithm. The two main ideas it employs are first, upper confidence bounds based on the Bernstein inequality and empirical variance estimates to compute the index based on which an arm is chosen at every round. Second, if an arm estimate is "far enough away" from the threshold as measured by the confidence bounds, it will be "eliminated", and no longer be pulled until the end of the budget. Both ideas are based not only on the empirical mean estimate $\mu_i(t)$, but also on a term $s_i$ that is increasing linearly in the estimated standard deviation. While the APT algorithm plays the arm minimizing the quantity $B_i^{APT}(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)$, AugUCB plays the arm minimizing the quantity $\hat{\Delta}_i(t) - 2s_i$, where $s_i$ is based on the variance estimate $\hat{v}_i$, and an exploration $\psi_m$ term linear in $T$, as well as an elimination parameter $\rho$ (compare Algorithm 1 in Mukherjee et al., 2017):

\begin{equation*}
s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}.
\end{equation*}

Consequently, the authors also introduce complexity measures which take the variance into account. From Gabillon et al. (2011) they use $H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}$. Furthermore, with $\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}$, where $\stackrel{\sim}{\Delta}_{(i)}$ is an increasing ordering of $\stackrel{\sim}{\Delta}_i$, the authors define a complexity corresponding to $H_{CSAR,2}$ in Chen et al. (2014):

\begin{equation*}
H_{\sigma,2} = \max_{i \in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
\end{equation*}

While the latter complexity appears in the provided upper bound on the AugUCB algorithm's expected loss, it could be replaced by $H_{\sigma, 1}$ since $H_{\sigma, 2} \leq H_{\sigma,1}$. $H_{\sigma,1}$ is more easily compared to the complexity $H$ defined in Locatelli et al. (2016). Essentially, every arm's complexity contribution is additionally scaled by a term increasing in the arm's variance (see also the graph comparing the complexity terms of APT, AugUCB, and EVT algorithms below).

In the case of the APT algorithm the number of times a specific arm has been drawn $T_i$ measures how concentrated the estimated mean is around the true mean (and thus for large $T_i$ an arm is no longer drawn even if $\hat{\mu}$ is close to $\tau$). This exploration is regulated by the combination of the variance estimate $\hat{v}_i$ and the exploration factor $\psi_m$ in the case of the AugUCB algorithm. The terms ensure that certain arms are no longer pulled when the algorithm is sufficiently confident in the location of true mean. Indeed, the AugUCB algorithm goes a little further than the APT algorithm in that it eliminates arms (no longer considers them in sampling) when a separation condition is estimated to hold. The same separation condition of estimated mean away from the threshold is used in the authors' upper bound proof and is reminiscient of the separation condition used in Locatelli et al.'s (2016) upper bound proof.

Therefore, when using a very similar favorable event in the proof of their upper bound, Mukherjee et al. (2017) have to bound the probability that an an arm is not removed from the active set after the a certain number of rounds -- even though the arm is above (respectively below) the threshold. If this probability is low, then the algorithm is able to be certain about an arm's true mean by employing variance estimates. In comparison, Locatelli et al (2016) used bounds on on how often arms are drawn ($T_i$) to give a bound on the probability of the favorable event. In order to derive the bound, Mukherjee et al. (2017) use the Bernstein inequality.

It has to be noted that Mukherjee et al. (2017) have to assume that the distributions have rewards bounded in $[0,1]$ in order to derive the bound on the probability that an arm has not been eliminated correctly in round $T_i$. Else it would not be possible to upper bound the $s_i$ term by $\Delta_i/4$ as Mukherjee et al. do in their proof. Thus, the distributions for which their upper bound holds are a subset of the $R$-sub-Gaussian distributions considered in Locatelli et al. (2016). However, while the authors demand in their setting that the rewards are bounded in $[0,1]$, it seems that the upper bound only requires the arms' variances to be bounded in $[0,1]$ such that $\hat{v}_i \in [0,1]$. Thus, the upper bound should hold in particular for Gaussian distributions with variance $\sigma^2 \in [0,1]$. Consequently, the simulations by Mukherjee et al. are performed on Gaussian arms with variance smaller than one.

@@

Compare Mukherjee et al. (2017) for the notation. Then it becomes clear that the left part of the RHS gives the probability that the mean estimate is out of wack, while the right term gives the probability that the variance is overestimated. The first term is bounded by the Bernstein inequality. In the cumulative regret setting, there exists a similar decomposition for algorithms based on upper confidence bounds. There, the expected number of pulls of a suboptimal arm is bounded. Compare for example chapter 3.1 in Kaufmann, Korda and Munos (2012), in which the authors decompose the expected number of draws of an suboptimal arm into the probability that the optimal arm's mean is underestimated, and the probability that the upper confidence bound of the suboptimal arm is still very large. To give bounds for UCB algorithms, certain convergence rates are shown for these two probabilities. Mukherjee et al. do similarly for their upper confidence algorithm in the thresholding setting.

@@

```{r EVT_Index_Bernoulli, echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center", out.width='80%', fig.cap = "This graph displays the distance part of the index of the APT, SLR, and EVT algorithms. While EVT's distance is based on both the empirical mean and empirical variance, the empirical mean determines the variance in the case of Bernoullis. We see that the distance of both EVT and SLR has an asymmetric behavior."}
bfun <- function(mu, tau) sqrt((mu*(1-mu))^2 + abs(tau-mu)) - mu*(1-mu)
KL_ber <- function(p,q) p*log(p/q) + (1-p)*log((1-p)/(1-q))
KL_gauss <- function(p,q) 2*(p-q)^2

evtdf <- data.frame(mu = seq(0.0000001,0.5,length.out = 10000),
                    tau = rep(0.1, 10000)) %>%
  mutate(APT = KL_gauss(mu, tau),
         SLR = KL_ber(mu, tau),
         EVT = bfun(mu, tau)) %>%
  gather(key = Algorithm, value = Distance, -mu, -tau) %>%
  mutate(tau = as.character(tau))

ggplot(evtdf, aes(x = mu, y = Distance, 
                  group = Algorithm, color = Algorithm,
                  linetype = Algorithm)) +
  geom_line() +
  labs(title = "Comparison of Distance Measures by Algorithm",
       subtitle = "For Bernoulli arms and a threshold at 0.1.",
       x = "Empirical Mean Estimate") +
  theme_bw() +
  theme(legend.position = "bottom")
```

@@

```{r Hevt_Hapt_Comparison, echo = FALSE, message = FALSE, fig.align="center", out.width = '80%', fig.cap = "This graph compares the complexity terms used in the APT, AugUCB, and EVT algorithms respectively. We observe that as the mean of the arm's distribution is closer to the threshold, the complexity of the problem increases much less rapidly for the EVT algorithm. Thus, the EVT should be able to cope with arms close to the threshold better than the APT algorithm. The complexity displayed for the AugUCB is an upper bound on the complexity used in the upper bound of Mukherjee et al. (2017)."}
hevt <- function(mu, tau) {
  (mu*(1-mu))^2 * (abs(mu-tau))^{-2} + abs(mu-tau)^{-1}
}

@@

haugucb <- function(mu, tau) {
  vars <- mu*(1-mu)
  (sqrt(vars) + sqrt(vars + (16/3)*(abs(mu-tau))))/(abs(mu-tau)^2)
}

hcompdf <- data.frame(mu = seq(0.1,0.9,length.out = 10000),
                      tau = rep(0.5, 10000)) %>%
  mutate(APT = hapt(mu, tau),
         EVT = hevt(mu, tau),
         AugUCB = haugucb(mu, tau)) %>%
  gather(key = Algorithm, value = Complexity, -mu, -tau)

ggplot(hcompdf, aes(x = mu, y = Complexity, group = Algorithm,
                    color = Algorithm, linetype = Algorithm)) +
  geom_line() +
  geom_vline(aes(xintercept = 0.5), linetype = 2) +
  ylim(c(0,400)) +
  theme_bw() +
  theme(legend.position = "bottom") +
  labs(x = "Mean", title = "Comparison of Complexity Terms",
       subtitle = "Complexity of single Bernoulli arm for APT and EVT and a threshold at 0.5.")
```

@@

# Experiments \label{chap:Experiments}

## Synthetic Data \label{sec:SyntheticData}

@@

```{r simulation1_results, echo = FALSE, fig.align = "center", out.width = '80%'}
library(ggplot2)
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR"), 
                   each = 1991), rep("B-UCB", 3991), rep("EVT", 1981))
index <- c(rep(10:2000, times = 4), 10:4000, 20:2000)
alg_res <- log(c(loc2_comp_UNIFORM_2000, loc2_comp_APT_2000, 
                 loc2_comp_AugUCB_2000, loc2_comp_LR_2000,
                 loc2_comp_BUCB_horizon_4000, loc2_comp_EVT))
loc2_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc2_comp_res, aes(x = index, y = results)) + 
  geom_line(aes(group = names, color = names)) +
  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  labs(title = "Results of Synthetic Experiment 1", 
       subtitle = expression(paste("Ideal scenario for APT; ", 
                                   tau,' = 0.5')), 
       y = "log(Error)", x = "Round Index") + 
  coord_cartesian(xlim = c(0,2000)) +
  scale_color_discrete(name = "Algorithm") + 
  theme_bw() +
  theme(legend.position = "bottom")

@@

```{r simulation2_results, echo = FALSE, fig.align = "center", out.width = '80%'}
library(ggplot2)
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"

@@

alg_names <- c(rep(c("Uniform", "APT", "AugUCB","SLR", "B-UCB"), 
                   each = 6991), rep("EVT", 6981))
index <- c(rep(10:7000, times = 5), 20:7000)
alg_res <- log(c(loc6nt_comp_UNIFORM_7000, loc6nt_comp_APT_7000,
                 loc6nt_comp_AugUCB_7000, loc6nt_comp_LR_7000,
                 loc6nt_comp_BUCB_horizon_7000, loc6nt_comp_EVT))
loc6nt_comp_res <- data.frame(index = index, names = alg_names, 
                            results = alg_res)
ggplot(loc6nt_comp_res, aes(x = index, y = results)) + 
  geom_line(aes(group = names, color = names)) +
  geom_hline(aes(yintercept = log(0.1)), linetype = 2) +
  labs(title = "Results of Synthetic Experiment 2", 
       subtitle = expression(paste("Difficult scenario for APT; ", 
                                   tau,' = 0.05 and 10 arms. Dashed line at Error = 0.1.')), 
       y = "log(Error)", x = "Round Index") +
  scale_color_discrete(name = "Algorithm") +
  theme_bw() + 
  theme(legend.position = "bottom")
```

```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%'}
load(file = "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/Thesis/experiment_postprocessing/loc6nt_ma.Rda")
library(dplyr)

rbind(loc6nt_APT_ma, loc6nt_LR_ma) %>%
  rename(Arm = arm) %>%
  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
  geom_line(size = 0.3) +
  facet_grid(.~algorithm) +
  labs(x = "Index", y = "10 Rounds Moving Average",
       title = "Average Number of Pulls Allocated to Each Arm per Round",
       subtitle = "5000 iterations; a value of 1000 means that in 20% of 
the iterations the arm was pulled in that round.") +
  theme_bw() +
  theme(legend.position = "bottom")
```

```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%'}
rbind(loc6nt_BUCB_c15_ma, loc6nt_BUCB_ma, loc6nt_BUCB_c5_ma) %>%
  rename(Arm = arm) %>%
  ggplot(aes(x = index, y = mean, group = Arm, color = Arm)) +
  geom_line(size = 0.3) +
  facet_grid(.~algorithm) +
  labs(x = "Index", y = "10 Rounds Moving Average",
       title = "Average Number of Pulls Allocated to Each Arm per Round",
       subtitle = "5000 iterations; a value of 1000 means that in 20% of 
       the iterations the arm was pulled in that round.") +
  theme_bw() +
  theme(legend.position = "bottom")
```

@@

```{r simulation3_results, echo = FALSE, fig.align = "center", out.width = '80%'}
library(ggplot2)
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/"

@@

```{r simulation4_results, echo = FALSE, fig.align = "center", out.width = '80%'}
library(ggplot2)
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/exponential/"

@@

```{r simulation5_results, echo = FALSE, fig.align = "center", out.width = '80%'}
library(ggplot2)
current_path <- "/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/synthetic_experiments/poisson/"

@@

```{r, echo = FALSE, message = FALSE, fig.align = "center", out.width = '80%'}
library(zoo)
library(tidyr)
library(dplyr)
library(ggplot2)
load("/Users/timradtke/Dropbox/1Master/Master Thesis/threshold-thesis/real_experiments/data_amo3_wide.Rda")

real_daily <- data.frame(index = 1:8641,
                                lapply(data_amo3_wide[1:10080,], FUN = rollapply, 
                                       width = 24*60, mean)) %>%
  gather(arm, mean, -index) %>%
  mutate(source = rep("Real", 86410)) %>%
  rename(Arm = arm)
